Seminar: Programming models and Code Generation\\ Winter Term 2014/2015\\ {\bf Quasi deterministic parallel programming using LVars}

### 2015-01-09 draft.tex
new

\textit{Idempotence,} meaning that $d\sqcup{d=d}$ for any element $d$. Repeated $puts$ or $freezes$ have no effect, if the scheduler is allowed to occasionally duplicate work, it is possible to save on synchronization costs. LVish computations are guaranteed to be idempotent and uses the scheduler(\textit{standard Chase-Lev deque}). Idempotence helps to deal with races between $put$ and $get/addHandler$. \\ \\ 

@@

The bag module supports atomic insertion and removal, and concurrent traversal.\\ \\
%\begin{verbatim}
\texttt{put :: Bag a -> a -> IO(Token a)\\
remove :: Token a -> IO() $\bot$\\
foreach :: Bag a ->\\
   (a -> Token a -> IO()) -> IO()}\\ \\
%\end{verbatim}

@@

The counter tracks the number of currently executing callbacks, which is used to implement quiesce. A bag of threads that are blocked waiting for the pool to reach a quiescent state. Please refer to\cite{lkuper2} for further details on the library implementation.\\ \\

@@

\caption{Performance of LVish on parallelizing k-CFA\cite{lkuper2}}

>>>>

\textit{Idempotence,} means that $d\sqcup{d=d}$ for any element $d$. Repeated $puts$ or $freezes$ have no effect and if the scheduler is allowed to occasionally duplicate work, it is possible to save on synchronization costs. LVish computations are guaranteed to be idempotent and use the scheduler(\textit{standard Chase-Lev deque}). Idempotence also 	helps to deal with races between $put$ and $get/addHandler$. \\ \\ 

@@

The bag module supports atomic insertion and removal, and concurrent traversal.
put :: Bag a -> a -> IO(Token a)
remove :: Token a -> IO() 
foreach :: Bag a ->
    (a -> Token a -> IO()) -> IO()

@@

The counter tracks the number of currently executing callbacks, which is used to implement quiesce. A bag of threads that are blocked waiting for the pool to reach a quiescent state.\\ Please refer to \cite{lkuper2}\cite{kuper} for further details on the library implementation and the different functions available.\\ \\ 

@@

\caption{Performance of LVish on parallelizing k-CFA\cite{lkuper2} and on a synthetic benchmark notChain.}
